In any network flow problem, of which transportation problems are a subset, the
cost of transporting commodities is what drives the solution. In other words,
costs are trying to be minimized, and it is the global minimization which
defines an optimal solution. Accordingly, an accurate cost function is
neccessary to determine an accurate solution. Because the \Cyclus simulation
environment is still a nascent technology, accurate pricing metrics, and what
such metrics even are in terms of a centuries-long fuel cycle simulation, are
not immediately available. Accordingly, the cost function is currently a measure
of simulation entity preference, rather than a concrete representation of cost.

The notion of preference extends the work of Kyle Oliver's affininty metric
\cite{oliver_geniusv2:_2009}. The preference metric is generally consumer
centric, i.e., consumers have a preference over the possible commodities that
could meet their demand. For example, a reactor may be able to use UOX or MOX
fuel, but may prefer to use MOX fuel. Herein lies the projection of real-world
cost into the simulation. Additionally, the managers of a given facility, which
in the \Cyclus simulation environment include its Institution and Region, also
exert an influence over its preference. An obvious example is the concept of
affinities given in \cite{oliver_geniusv2:_2009}. In Oliver's work, an affinity
or preference existed between facilities in ``similar'' institutions in order to
drive the trading between institutions as a simple model of international
relations. I expand upon this idea to cover a facility's other managers and
the commodities themselves. Additionally, a preference can be delineated between
the proposed qualities of the same commodity from different vendors. Finally,
the notion of a preference is a positive one, and we require a notion of cost to
solve the minimum-cost formulation of the multicommodity transportation problem
with side constraints. Therefore we must have a translation function.

Formally, we define a preference function, which is a cardinal preference
ordering over a consumer's satisfying commodity set.

\begin{equation}
\alpha_{i,j}(h) \: \forall i \in I \: \forall h \in H_{j} 
\end{equation}

This ordering is a function both of the consumer, $j$, and producer, $i$. The
dependence on producer encapsulates the relationship effects due to managerial
preferences. We then define a cost translation function, $f$, that operates on
the commodity preference function to produce an appropriate cost.

\begin{equation}
f : \alpha_{i,j}(h) \to c_{i,j}^{h}
\end{equation}

A naive implementation, and perhaps all that is necessary for a
proof-of-principle, is to define f as an inversion operator.

\begin{equation}
f(x) = \frac{1}{x}
\end{equation}

The necessity for complexity of this translation function is not immediately
obvious and an analysis will be performed to understand its impact.
