Fuel cycle simulators have a number of possible output metrics of interest, and
the Department of Energy has initiated a number of exercises to discuss them
through its Used Fuel Disposition campaign \ref{nutt_proposed_2012,
taiwo_summary_2012}. One of the original reasons that fuel cycle simulators were
developed was to determine the relative cost of different fuel cycles. The
notion of fuel cycle cost can either be calculated in a post-processing step, or
it can be calculated on-the-fly during a simulation. The benefit of maintaining
cost information during a simulation is that the simulation can react to these
costs. A prime example of such behavior is in the DANESS simulation code,
described in \S\ref{sec:other-sims}. Other simulators, such as VISION, determine
costs at the end of a simulation based on all events in the simulation using
values from AFCI cost basis report
\cite{yacout_vision_2006,shropshire_advanced_2007}. It must be stressed that the
notion of predicting future fuel cycle costs have a high degree of
variability. They depend not only on the level of maturity of technologies as a
function of time (i.e., the R\&D investment level for the technology), but also
on material costs which are relatively unknown and/or very hard to
predict. Accordingly, it helps to determine relative costs of fuel cycles rather
than absolute costs of fuel cycles. Further, it helps to classify fuel cycles by
the technology used in them.

The fuel cycle cost metric provides a prime example of a key choice of
developers of fuel cycle simulators. Most metrics outside the actual
instantiation of facilities (i.e., which facilities are built when) and the flow
of material, which are integral to the running of the simulation, can be post
processed. They are only required to be maintained during the simulation if the
some aspect of the simulation depends upon them. Accordingly, unless decisions
are being made on the basis of costs, there is no reason to maintain a cost
metric at simulation time. Simulators can generally be divided into two groups,
those that make decisions at run time based on certain metrics and those that do
not. \Cyclus is designed to provide dynamic support of metric-based decision
making, e.g., Huff's recent work with dynamic repository capacity determination
\cite{huff_integrated_2013}.

A large number of metrics related to fuel cycle simulation come directly from
the material mass flows. For instance, proliferation based metrics are generally
determined by the amount of separated transuranic material at any point in the
fuel cycle. Metrics that lead to less proliferation resistance include the
amount of significant quantities of material, defined by the IAEA to be the
quantity of any given material (e.g., TRU or plutonium) sufficient to make a
nuclear weapon. These are generally defined on the elemental level, which
ignores realities based on isotopic dependencies (e.g., \nucl{240}{Pu} is a
relatively large source of decay heat and is thus reduces the aggregate
plutonium's effectiveness for use as a weapon). Metrics that lead to more
resistance of proliferation activities include the unshielded dose rate of a
given material, which makes handling (and thus diverting) the material more
difficult \cite{yacout_vision_2006}. Another key metric that is important to
many in the fuel cycle simulation community is uranium utilization. At present,
the United States political stance is to continue the once-through fuel cycle
until it is economically viable to begin reprocessing spent fuel for recycle in
reactors \cite{hamilton_blue_2012}. Such a situation can only arise if the
supply of uranium dwindles to a low-enough level which will raise the price of
uranium sufficiently to make reprocessing a viable alternative. It is
additionally interesting to note the approximate time at which uranium capture
from sea water, which is in developmental stages, will become economically
viable. These situations all depend on the amount of uranium used in a given
simulation, which is, of course, related to fuel mass flows.

Another key output of simulators is related to repository capacities. The
capacity a repository to store spent fuel could be reached in a number of
ways. Spent fuel isotopics, especially fission products, produce a large amount
of decay heat which can reach the thermal limits of their containers over short
periods of (geologic) time. There are also radiotoxicity limits for repositories
in order to limit the risk of radiological releases. Finally, there are mass and
volume limits on repositories, representing a space storage capacity. In fact,
the Nuclear Waste Policy Act, the current U.S. law determining the U.S.'s used
fuel management strategy, places a blanket mass capacity limit of 70,000 t on
Yucca Mountain \cite{us_nuclear_1982}.  It is not clear at the current time
which of these limiting capacities will ultimately be the governing
engineering-based limiting factor for repositories. Furthermore these capacities
change based on repository layout and geology.  This parameter was key in
Scopatz's work with static fuel cycle simulation
\cite{scopatz_essential_2011}. In all cases, these capacities can be calculated
in terms of isotopic quantities of waste products. It is possible to calculate
the capacity parameters \textit{in situ} during the simulation, shown by Huff in
\cite{huff_integrated_2013} and dynamically alter the simulation based on the
results rather than simply performing a post-processing operation to report the
required number of repositories for the simulation.
