\subsection{Using Agent-Based Models}

Stepping back a moment from the discussion of nuclear-specific fuel cycles, the
interactions that we wish to model are those of supply and demand. Certain
facilities need some sort or raw or processed material that other facilities
produce. The fuel cycle is more complicated than this simple statement, though,
because facilities are connected through recycled fuel. Even with such a
complication, the notion of a generic fuel cycle, i.e. from the perspective of
facilities that supply and demand material, quickly begins to look like a supply
chain model. There is a growing literature of agent-based supply chain modeling
\cite{swaminathan_modeling_1998,julka_agent-based_2002,van_der_zee_modeling_2005,chatfield_multi-formalism_2007,holmgren_agent_2007}.
The general premise of these types of models is that individual facilities have
a notion of their needs (i.e., their demands) and can express to the system
these needs at the required time. There is heavy use of inventory policy to
determine the correct amount of material inventory that is needed and the
correct time to request a resupply. In general, a facility may be comprised of
many agents, e.g. an ordering agent, a stocking agent, a forecasting agent,
etc. Such an approach has not heretofore been attempted for the nuclear fuel
cycle and opens up a variety of doors. For example, reactor facilities could be
allowed to be fueled by multiple fuel types (e.g., UOX or MOX), and decide which
type to choose based on the simulation environment. However, due to the
fungibility of material in the fuel cycle (plutonium, for instance, can be used
by fast reactors and thermal reactors), many questions remain about how to
describe the materials to be traded and the markets on which they will be
traded. A more fully formed proposal for such a treatment is presented in
\S\ref{sec:gfctp}.

\subsection{Input Fuel Isotopic Matching}

One of the major issues with current fuel cycle simulation is the disconnect
between fuel recipes being requested by reactors that need recycled fuel,
e.g. MOX fuel. The isotopics that comprise these materials, especially the
transuranic isotopes, are radioactive, and thus the actual isotopic composition
of material change with time. Accordingly, if a simulator wishes to try to match
the requested isotopics, it must keep track of the decay of isotopes. Further
complicating the problem is that requested input fuel recipes may not
necessarily be related to the provided output fuels, i.e., there is a mismatch
between the output isotopics and input isotopics even without the presence of
isotopic decay. The majority of fuel cycle simulators to date ignore this issue
and instead choose to match recipes ``exactly'' based on a subset of
isotopes. Further details of how other simulators tackle this issue are reviewed
in \S\ref{sec:simulators}. A full treatment of the recipe-matching problem would
require an approach similar to the pooling-blending problem
\cite{tawarmalani_convexification_2002}. There is a rich literature base for
pooling-blending problems
\cite{glen_mixed_1988,rigby_evolution_1995,mendez_simultaneous_2006,misener_advances_2009}
in the industrial processes literature. However, the majority of the subject
matter concentrates on refinery operations such as mixing various crude oils to
hit a certain octane level. These are (relatively) simple problems because the
properties that are trying to be matched are extrinsic and linear function of
the mixing variables. The nuclear arena is much more complicated because of
criticality limitations and the want to match aggregate nuclear properties of
materials. Accordingly, a hybrid approach was proposed that involves blending and
approximation theory. The approach is outlined in \S\ref{sec:rap}.

\subsection{Modeling Global Regions}

The notion of regional modeling in fuel cycle simulation has always been a
secondary concern. Certain simulators attempt to model it explicitly, e.g. DESAE
\cite{iaea_nuclear_2010}. Other simulators have attempted to add the capability
at some point after their simulator had already been developed, e.g. VISION and
COSI. A discussion of these capabilities follows in \S\ref{sec:simulators}. Some
semblance of this capability is needed if one is to incorporate outside effects
on a domestic fuel cycle. Furthermore, a robust capability is required if one
wishes to actually investigate dynamic interactions amongst regional
entities. Again, a full treatment of this sort of regional interaction would
require international relations models, most of which can be found in the
cross-cutting realm of economics, political science, and game theory. The
primary solution technique is called Nash Equilibrium, and effectively describes
an optimal solution as follows: given a set of players, states, preferences,
and actions, all players choose an action such that any single player's
deviation from that actions results in a state of lower preference for that
player (thus no player has an incentive to deviate)
\cite{mccarty_political_2007}. There also exists a body of literature that
examine Nash Equilibria in the context of optimal flow models
\cite{mazumdar_fairness_1991,nagurney_supply_2002,song_nash_2002}. However, the
complexity of such models quickly brings them out of the scope of our needs,
i.e., dynamic modeling of multi-lateral scenarios ranging 100+ years in a
short-time ($\sim$2-5 minutes). Accordingly, a market resolution mechanism has
been proposed that allows for interaction amongst the various facilities and
managing entities (e.g. their regions). In order to inform a cardinal preference
\cite{strotz_cardinal_1953} relation for a facility over its possible supply
materials. The full approach is outlined in sections \S\ref{sec:gfctp} and
\S\ref{sec:agent-interaction}.
