\chapter{Simulation and Agent Based Modeling in Cyclus}\label{ch:abm}

Developing a simulator of any complex system is an involved process requiring a
solid methodological base. A reasonable approach is to define precisely the
simulation framework, including a definition of how time moves forward and what
events can occur. This chapter lays the foundation for the simulation of nuclear
fuel cycles in Cyclus. \secref{abm:sim} begins the discussion by broadly
describing methodological principles on which Cyclus has been developed. The use
of agent-based modeling techniques is presented in \secref{abm:abm}, and an
agent deployment methodology with a proof-of-principle benchmark is
presented. Finally, \secref{abm:dre} treats the most complex simulation
interaction in Cyclus, Dynamic Resource Exchange (DRE), describing its
methodology, discussing its implementation, and presenting a set
proof-of-principle results.

\input{./chapters/2-abm/sim}

\input{./chapters/2-abm/abm}

\input{./chapters/2-abm/dre}

\section{Summary}

This chapter introduced a novel way to employ agent-based modeling techniques in
the nuclear fuel cycle. \secref{abm:sim} first described how a simulation is
structured, focusing on where agent interactions occur in a given time step. A
discussion of how the notion agency is applied to fuel cycle entities and a
proof-of-principle simulation was shown in \secref{abm:abm}. Finally, a detailed
description of a novel supply-demand, agent-based framework, the DRE, was
presented in \secref{abm:dre}. The DRE is a critical advancement in the realm of
nuclear fuel cycle simulation, enabling arbitrary facility-based constraints,
competition for fungible resources, and the application of socio-economic models.
